Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-11 delegations.tex
Write TODO on security
Change wording

We start by constructing a verifiable long output scheme. Then, we encrypt the scheme as given in \cite{mahadev_delegation} to achieve security. TODO Does it actually work though? There are multiple steps in the scheme... We encrypting each step separately or what?

>>>>

We start by constructing a verifiable long output scheme. Then, we encrypt the scheme as given in \cite{mahadev_delegation} to achieve security. That is, we first encrypt the circuit. Then TODO it's not immediately obvious that this works. This isn't purely a circuit anymore, but we also have classical data and evaluation key now.
